---
title: "flywire_MIP"
author: "Tomke Stuerner"
date: "08/07/2021"
output: html_document
---
```{r, message=FALSE}
library(natverse)
library(fafbseg)
library(elmr)
library(nat.jrcbrains)
```

```{r flywire}
choose_segmentation("flywire31")
catmaid_login() #this only works if you have your credentials saved in your environment
```

```{r define the JRC2018U MIP}
# define the JRC2018U MIP version as a templatebrain object:
JRC2018Umip = templatebrain("JRC2018Umip", dims = c(1210,566,174), voxdims = c(0.519,0.519,1), units = "microns")
```

```{r load neuron and tranform}
# load your neuron (swap this to fafbseg::skeletor("seg_id") to get FW neuron)
# LC_uDNb05 =  read_cloudvolume_meshes("720575940630813779")
# LHPV10d1 =  read_cloudvolume_meshes("720575940616289605")
# ALBN1 =  read_cloudvolume_meshes("720575940634330231")
# MBDL1 =  read_cloudvolume_meshes("720575940639208949")
# mALB1 =  read_cloudvolume_meshes("720575940613406786")
# M_spPN5t10 =  read_cloudvolume_meshes("720575940628217564")
# M_ilPN8t91 =  read_cloudvolume_meshes("720575940615488916")
# M_ilPNm90 =  read_cloudvolume_meshes("720575940616942494")
# M_ilPN = c("720575940616942494","720575940615488916" )
AL_nosoma = read_cloudvolume_meshes("720575940604860802")
# transform it to JRC2018U template
AL_nosoma.JRC2018U = xform_brain(AL_nosoma, sample = "FAFB14", reference = JRC2018U)

# create a 3d image from this (a 3D matrix, with 1s where the skeleton goes and 0s where there is no skeleton)
# the only trick is that here we use the MIP brain template, to get the right dimensions for the output
im = as.im3d(xyzmatrix(AL_nosoma.JRC2018U), JRC2018Umip)

# write out a nrrd file
# dir.create("flywire_MIP")
write.im3d(im, paste( "./flywire_MIP/AL_nosoma.JRC2018U.nrrd"))
# after you have this nrrd open it in Fiji
```

# I normally adjust the image until I can see the neuron (it's very thin so it's a bit tricky)
# then I run 3D gaussian blur with 2 pixel radius, then readjust to have a reasonable width for the neuron (press apply in the image adjustment window)
# after this you can run create the MIP (mean intensity projection) with the right color coding 2 ways:
# wither use their plugin https://github.com/JaneliaSciComp/ColorMIP_Mask_Search (this doesn't work for me for whatever reason)
# or run Image/Hyperstacks/Temporal color code and pick the "PsychedelicRainbow2" as a LUT -  this you also have to download from their github repo and put it in the right Fiji folder
# save as a tif and upload on neuronbridge to find light level matches